\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Mike}
\familyname{\mbox{Orlov}}
\email{pmapcat@gmail.com}
\social[linkedin]{pmapcat}
\social[github]{pmapcat}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% command and color used in this document, independently from moderncv 
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
\renewcommand{\labelitemi}{$\circ$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-1cm}

\section{\textsc{Professional Experience}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
		\cventry{May. 2019 - present}{Backend dev}{Kasta.ua}{Kyiv, Ukraine}{}{
		  {\footnotesize
			  \begin{itemize}
			  \item Developed and owned product upload and validation. As per public info, we've had over two million products and over 11 million users.
                          \item Designed, implemented, and documented public-facing API.
                          \item Worked with business, QA, frontend, and cross-team to deliver significant features.
                          \item Refactored and optimized existing code, resolved support issues, and fixed bugs. Helped with feature design, onboarding, and code reviews. 
                          \item Tech: PostgreSQL; SQL;  Clojure; ClojureScript; React; Rum; JavaScript; APIs; Unix tools; Excel; Apache POI; Jira; Frontend; Backend; Fullstack; Emacs; Git; Gitlab; Sentry; Kibana; Grafana; Kafka; Queues; Elastic; Confluence; s3
			  \end{itemize}
			}
		}
		\cventry{Apr. 2018 - Mar. 2019}{Software dev}{Contract work}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Made an antique book management platform with integrations with several marketplaces, a shipping calculator, and a website for a recruiting agency.
                                \item Tech: Rest Api; XML Api; SQLite3; Python; DRF; Django Admin; Clojure; Digital Ocean; PureCSS; HTML; CSS; JS  
				\end{itemize}
			}
		}
		\cventry{April. 2016 - April. 2018}{Software dev}{Bookline}{Jerusalem, Israel (Remote)}{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked for a company in Jerusalem doing in-house, public-facing, and some outsource work.
                                \item Made a time tracker SPA website, a landing page constructor, an antique book exchange website, and a generator of static wiki pages.
                                \item Did data scraping, cleaning, linking, and transforming to prepare for ingestion by other systems.
                                \item Helped with hiring and onboarding.
                                \item Tech: Go; Golang; POS Tagger; Viterbi; SMT Moses; TFIDF; SQLite3; Go Json Rest; Clojure; Lucene; SPA; ClojureScript; React; Elastic; MaterializeCSS; Django Admin; HoneySQL; API; MediaWiki  
				\end{itemize}
			}
		}
		\cventry{Nov. 2015 - Feb. 2016}{Software dev}{Contract work}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Made a book store web site with integrations with an external payment system and several online marketplaces; A landing for a car wash in Israel; A landing page for a shop selling antique engravings;
                                \item Tech: Go; Golang; MySQL; Express; DigitalOcean; MaterializeCSS; JavaScript; Bootstrap; CSS; Python; JS; JQuery; React; CoffeeScript; TypeScript; ClojureScript  
				\end{itemize}
			}
		}
		\cventry{Apr. 2013 - July. 2013}{Backend dev}{Rarebooks.ru}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Migrated the backend and the data from legacy PHP platform to Python Django with Haystack (using Elastic) and MySQL. Made an integration with online marketlace.
				\end{itemize}
			}
		}
		\cventry{Jun. 2012 - Dec. 2015}{Techical Co-founder (part time)}{}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Worked on a video editing and tagging platform together with a non-technical co-founder.	
				\end{itemize}
			}
		}


\section{\textsc{Education}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{}{2014}{}{BSc Economics, Russian Technological University (MIREA)}{}{}
                
                
\section{\textsc{Other Personal Projects}}
		\cvitem{\textbullet}{Writing OSS and Certificates}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
                                \item 2023, \textbf{CEFR C1} in the EnglishScore Core Skills test {\color{see} \href{https://api2.englishscore.com/verify/0b056e3c}{link}}
                                \item 2019, Wrote on Quora about Programming, Web Dev, Languages, Python, JS. Answers reached \textbf{2.3 million} people {\color{see} \href{https://www.quora.com/profile/Michael-6688}{link}}
                                \item 2018, Autocomplete widget {\color{see} \href{https://github.com/pmapcat/reagent_autocomplete}{link}}
                                \item 2016, File location toy {\color{see} \href{https://github.com/pmapcat/gokinate}{link}}
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
\end{document}
%% end of file `page.tex'.
